### 2013-07-19 doc/asplos14/overview.tex
take a stab at making the overview intro more compelling and tell our story

\Grappa leverages as much freely available and commodity infrastructure as
possible. We use unmodified Linux for the operating system and an
off-the-shelf user-mode InfiniBand device driver stack~\cite{OFED}. MPI is
used for process setup and tear down. GASNet~\cite{gasnet} is used as the
underlying mechanism for remote memory reads and writes using active message
invocations. To this infrastructure, \Grappa adds  three main software components, shown in Figure~\ref{fig:grappa}:

@@

\item[Communication layer.] The main goal of our communication layer is to
aggregate small messages into large ones.  This process is invisible to the application
programmer. Its interface is based on active messages~\cite{vonEicken92}.
Since aggregation and deaggregation of messages needs to be very efficient, we perform the process in parallel and carefully use lock-free synchronization
operations.

>>>>

Commodity hardware systems provide fast processors and high-bandwidth
interconnects but suffer when they encounter unpredictable data access
patterns. Maximizing throughput in such a situation depends upon proper
management of concurrency and communication. The \Grappa runtime
components handle thousands of concurrent accesses and batch them to
efficiently use the network. The imbalance between network bandwidth
and core-cycles for communication-intensive codes makes supporting
these functions in software an attractive design point. 
\Grappa specifically employs user-mode threading and networking for
low overhead because context switches and messages are very frequent.

As \Grappa depends on concurrency for performance, its programming
model focuses on enabling programmers to express large amounts of
concurrency. The overall goal is for the system to provide the
critical components for a well-performing implementation of an
irregular application, allowing the programmer to foremost focus on
expressing concurrency. While the programmer can initially be
productive in a shared memory environment and rely on the
underlying runtime components for reasonable performance, \Grappa
provides constructs for optimizing for locality and overlapping
communication.

\Grappa comprises three main software components, shown in Figure~\ref{fig:grappa}:

@@

\item[Communication layer.] The main goal of our communication layer is to
aggregate small messages into large ones.  This process is invisible to the application
programmer. Its interface is based on active messages~\cite{vonEicken92}.
Since aggregation and deaggregation of messages needs to be very efficient, we perform the process in parallel and carefully use lock-free synchronization
operations.
\TODO{Re-include the mention of GASNET,MPI spawning,and inifiniband
    somewhere but not in the overview intro}
